<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{rtimes vignette}
%\VignetteEncoding{UTF-8}
-->

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

rtimes vignette - R client for New York Times APIs
======

## About the package

`rtimes` is an R package to search and retrieve data from the New York Times congress API.

Functions in `rtimes` that wrap these APIs are prefixed by two letter acronyms fo reach API + the function name itself, e.g.: `cg` + `fxn`

* `cg` for the [Congress API](https://propublica.github.io/congress-api-docs)
* `as` for the [Article Search API](http://developer.nytimes.com/article_search_v2.json)
* `cf` for the [Campaign Finance API](https://propublica.github.io/campaign-finance-api-docs)
* `geo` for the [Geographic API](http://developer.nytimes.com/geo_api_v2.json)

Please get your own API keys at http://developer.nytimes.com/apps/register - you'll need a different key for each API.

I set up the functions so that you can put the key in your `.Renviron` file, which will
be called on startup of R, and then you don't have to enter your API key for each run
of a function. Add entries for an R session like

```
Sys.setenv(NYTIMES_GEO_KEY = "YOURKEYHERE")
Sys.setenv(NYTIMES_AS_KEY = "YOURKEYHERE")
Sys.setenv(PROPUBLICA_API_KEY = "YOURKEYHERE")
```

Or set them across sessions by putting entries in your `.Renviron` file like

```
NYTIMES_GEO_KEY=<yourkey>
NYTIMES_AS_KEY=<yourkey>
PROPUBLICA_API_KEY=<yourkey>
```

You can also pass in your key in a function call, but be careful not to expose your keys in
code committed to public repositories. If you do pass in a function call, use e.g., `Sys.getenv("NYTIMES_GEO_KEY")`.

## Install rtimes

From CRAN

```{r eval=FALSE}
install.packages("rtimes")
```

Development version from GitHub

```{r install, eval=FALSE}
install.packages("devtools")
devtools::install_github("ropengov/rtimes")
```

## Load rtimes

```{r load}
library('rtimes')
```

_Note: Member ID S001181 is Jeanne Shaheen_

## Congress API

### Bill cosponsorship data for a member

```{r cg_billscosponsor}
out <- cg_billscosponsor(memberid='S001181', type='cosponsored')
out$data
```

### Member appearances

```{r cg_memberappear}
out <- cg_memberappear(memberid='S001181')
out$data
```

## Article search API

This function in most cases outputs a series of S3 objects, one for each item
found. Each element, an object of class `as_search`, is a summary of a list
of data. You can `unclass()` the object if you want, or index into particular
elements (see egs below).

Here, we search for _bailout_ between two dates, Oct 1 2008 and Dec 1 2008

```{r}
res <- as_search(q="bailout", begin_date = "20081001", end_date = '20081201')
res$copyright
res$meta
res$data
```

Another e.g., Search for keyword _money_, within the _Sports_ and _Foreign_ news desks

```{r}
res <- as_search(q = "money", fq = 'news_desk:("Sports" "Foreign")')
res$data
```

## Campaign Finance API


Here, we search for campaign details for the 2008 cycle, with FEC ID number P80003338

```{r}
cf_candidate_details(campaign_cycle = 2008, fec_id = 'P80003338')
```

## Geographic API

The geographic API allows you to do geo based searches of place names. It's built on
the Geonames database.

Here, we search for results for locations in the US

```{r}
geo_search(country_code = 'US')
```
