<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{rtimes vignette}
-->

rtimes vignette - Interface to the New York Times APIs for government data.
======

### About the package

`rtimes` is an R package to search and retrieve data from the New York Times congress API. 


#### Install rtimes

```{r install, eval=FALSE, echo=TRUE}
install.packages("devtools")
library(devtools)
install_github("rtimes", "ropengov")
```

********************

#### Load rtimes

```{r load, comment=NA, warning=FALSE, message=FALSE}
library(rtimes)
```

*Note: Member ID S001181 is Jeanne Shaheen*

#### Get bill cosponsorship data for a particular member.

```{r cg_billscosponsor, comment=NA, warning=FALSE, message=FALSE, cache=TRUE}
out <- cg_billscosponsor(memberid='S001181', type='cosponsored')
ldply(out$results[[1]]$bills, function(x) data.frame(x[c('number','cosponsors')]))
```

#### Get information about a particular member's appearances on the House or Senate floor.

```{r cg_memberappear, comment=NA, warning=FALSE, message=FALSE, cache=TRUE}
library(plyr)
out <- cg_memberappear(memberid='S001181')
ldply(out$results[[1]]$appearances, function(x) data.frame(x[c('date','title')]))
```